sensiAnPaper1All

### 2016-01-20 effectOfIndividualInputs.Rmd
remove from plots runs where thresholds not reached

>>>>

  #remove runs that didn't reach a resistance threshold (999), even if just for one strategy
  #>1000 excludes sequential strategy that had a 999 in
  #BEWARE would need to increase 1000 if I increase max generations in the runs
  didntReachThresh <- which(ggInsOuts$gen_cP0.5 == 999 | ggInsOuts$gen_cP0.5 > 1000 |
                            ggInsOuts$gen_cP0.25 == 999 | ggInsOuts$gen_cP0.25 > 1000 |
                            ggInsOuts$gen_cP0.1 == 999 | ggInsOuts$gen_cP0.1 > 1000 )

  #subset by runs not making threshold
  ggInsOuts <- ggInsOuts[-didntReachThresh,]
